Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-03-12 msc-publication.tex
plot meshes for MWR paper
introduce the tests we're performing

\begin{figure*}
	\centering
	TODO
	%
	\caption{Examples of (a) BTF, (b) SLEVE, and (c) a cut cell grid, all constructed with OpenFOAM.  The two dimensional grids are \SI{20}{\kilo\meter} wide and \SI{2}{\kilo\meter} high.  The cut cell grid was created by intersecting the terrain surface with a regular grid as described in section~\ref{sec:grid}.}
	\label{fig:grid}
\end{figure*}

@@

\section{Results}
A series of standard, two-dimensional tests were performed over idealised orography.  For each test, results on the BTF, SLEVE and cut cell grid are compared.
We use a finite volume discretisation of the fully-compressible Euler equations described by \citet{weller-shahrokhi2014}.  The model has a curl-free pressure gradient formulation, an upwind-biased cubic advection scheme, and uses a Lorenz staggering of thermodynamic variables.  No explicit diffusion is used in any of the tests.

@@

\begin{table}[t]
	\caption{\TODO{add terrain-following results to this table} Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the tracer advection test.  Results of the cubic upwind-biased scheme are compared with the fourth-order centred scheme from \citet{schaer2002}.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ l l l l l l }
\hline\hline
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& \(\ell^2\) error & min & max & min & max \\
\hline
Analytic  & 0 & 0 & 1 & 0 & 1 \\
BTF 	  & \num{-1} & \num{-1} & \num{-1} & \num{-0.058} & \num{1.001} \\
SLEVE 	  & \num{-1} & \num{-1} & \num{-1} & \num{-0.002} & \num{0.984} \\
Cut cell  & \num{-1} & \num{-1} & \num{-1} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
No orography & \num{-1} & \num{-1} & \num{-1} & \num{-0.002} & \num{0.984} \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-meshes/fig-meshes.pdf}
	%
	\caption{Examples of (a) BTF, (b) SLEVE, and (c) a cut cell grid, all constructed with OpenFOAM.  The two dimensional grids are \SI{20}{\kilo\meter} wide and \SI{2}{\kilo\meter} high.  The cut cell grid was created by intersecting the terrain surface with a regular grid as described in section~\ref{sec:grid}.}
	\label{fig:grid}
\end{figure*}

@@

\section{Results}
A series of standard, two-dimensional tests are performed over idealised orography.  For each test, results on the BTF, SLEVE and cut cell grid are compared.  The first test from \citet{schaer2002} advects a tracer in a horizontal velocity field.  Second, a new tracer advection test is formulated employing a terrain following velocity field to challenge the advection scheme on more orthogonal grids.  The third test solves the Euler equations for a stably stratified atmosphere at rest, following \citet{klemp2011}.  Finally, as specified by \citet{schaer2002}, a test of orographically-induced gravity waves is performed.

We use a finite volume discretisation of the fully-compressible Euler equations described by \citet{weller-shahrokhi2014}.  The model has a curl-free pressure gradient formulation, an upwind-biased cubic advection scheme, and uses a Lorenz staggering of thermodynamic variables.  No explicit diffusion is used in any of the tests.

@@

\begin{table}[t]
	\caption{\TODO{add terrain-following results to this table or put in separate table?} Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the tracer advection test.  Results of the cubic upwind-biased scheme are compared with the fourth-order centred scheme from \citet{schaer2002}.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ l l l l l l }
\hline\hline
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& \(\ell^2\) error & min & max & min & max \\
\hline
Analytic  & 0 & 0 & 1 & 0 & 1 \\
BTF 	  & \num{-1} & \num{-1} & \num{-1} & \num{-0.058} & \num{1.001} \\
SLEVE 	  & \num{-1} & \num{-1} & \num{-1} & \num{-0.002} & \num{0.984} \\
Cut cell  & \num{-1} & \num{-1} & \num{-1} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
No orography & \num{-1} & \num{-1} & \num{-1} & \num{-0.002} & \num{0.984} \\
\hline
\end{tabular}
\end{table}
